Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2022-05-05 FDT2020/Introduction.tex
Some edits around non-negativity of c, typo fixes, etc.

The reason that we define integrality gap for a polyhedron as opposed to an instance of a problem is that our algorithms are independent of the cost function $c$.

@@

\begin{thm}[Carr, Vempala \cite{Carr2004}] \label{CV2}
	We have $g(I) \leq C$ if and only if for $x\in P(I)$ the vector $Cx$ can be is as a convex combination of points in $\dom(S(I))$. 
\end{thm}
Goemans \cite{goemansblocking} first introduced Theorem \ref{CV2} for blocking-type polyhedra. While there is an exact algorithm for problems with gap $1$, as stated in Proposition \ref{cara}, Theorem~\ref{CV2} is existential, with no construction. We remark that Proposition \label{CV2} would not work if we drop the non-negatvitiy constraints on the cost function $c$ in the definition of integrality gap (Defitinon \ref{IGofPoly}).
%In contrast to Proposition \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time.
%This points to an interesting open question. 
% We show later, for $I$ with $g(I)<\infty$, the notation of dominant is in fact useful.
\iffalse

@@

Carr and Vempala \cite{metarounding} showed if there an algorithm $\mathcal{A}$ that for $I\in \mathcal{I}$ and $c\geq 0$ finds $z\in S(I)$ with $cz\leq g'cx$ for any $x\in P(I)$, then $g'x$ can be \textbf{write} as a convex combination of points in $S(I)$. However, for many known problems there is a gap between the best known $g'$ and $g(\mathcal{I})$.

>>>>

The reason that we define integrality gap for a polyhedron as opposed to an instance of a problem is that our algorithms are independent of the cost function $c$. We do, however, require the cost function $c$ to be non-negative since that is required to use the Carr-Vempala theorem, as described below.

@@

\begin{thm}[Carr, Vempala \cite{Carr2004}] \label{CV2}
	We have $g(I) \leq C$ if and only if for $x\in P(I)$ the vector $Cx$ can be expressed as a convex combination of points in $\dom(S(I))$. 
\end{thm}
Goemans \cite{goemansblocking} first introduced Theorem \ref{CV2} for blocking-type polyhedra. While there is an exact algorithm for problems with gap $1$, as stated in Proposition~\ref{cara}, Theorem~\ref{CV2} is existential, with no construction. Proposition~\label{cara} would not work if we drop the non-negativity constraints on the cost function $c$ in the definition of integrality gap (Definition~\ref{IGofPoly}).
%In contrast to Proposition \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time.
%This points to an interesting open question. 
% We show later, for $I$ with $g(I)<\infty$, the notation of dominant is in fact useful.
\iffalse

@@

Carr and Vempala \cite{metarounding} showed if there an algorithm $\mathcal{A}$ that for $I\in \mathcal{I}$ and $c\geq 0$ finds $z\in S(I)$ with $cz\leq g'cx$ for any $x\in P(I)$, then $g'x$ can be written as a convex combination of points in $S(I)$. However, for many known problems there is a gap between the best known $g'$ and $g(\mathcal{I})$.
